% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[11pt,margin,line]{res}

\textwidth=6.3in
\textheight=10.45in
\sectionskip=0.12in
\parskip=0.12in
\addtolength{\oddsidemargin}{-0.475in}
\addtolength{\topmargin}{-.775in}

\usepackage{hyperref}
\usepackage{enumitem}

\newcommand{\bulletindent}{11pt}
\newcommand{\CC}{C\nolinebreak\hspace{.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}

\begin{document}

\name{\LARGE\bf Fang Zhou}

\begin{resume}

\section{Contact}
\href{github.com/t1mch0w/}{https://github.com/t1mch0w/}
\hfill \href{mailto:timchou.hit@gmail.com}{timchou.hit@gmail.com} \hfill (614)-329-1184  %\hfill 547 Riverview Dr., Apt A2, Columbus, OH, 43202

\section{Education}
{\bf The Ohio State University.} Columbus, OH       \hfill 2015 - Present\\
{\bf Ph.D. in Computer Science and Engineering}, GPA 3.9/4  \hfill Expected May.2020

{\bf Auburn University.} Auburn, AL \hfill 2013 - 2015\\
{\bf M.S. in Computer Science and Software Engineering}, GPA 3.9/4 
\begin{itemize}[leftmargin=\bulletindent]
	\itemsep -2pt
    \item Woltosz Fellowship 2013-2015 
\end{itemize}

{\bf Harbin Institute of Technology.} Harbin, China \hfill 2010 - 2012\\
{\bf M.S. in Computer Science} 

{\bf Central South University.} Changsha, China \hfill 2006 - 2010\\
{\bf B.S. in Computer Science} 

\section{Working Experience}
{\bf Parallel Architecture \& Systems Lab. Auburn, Research Assistant}   \hfill 2013 - 2015
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
        \item {\bf Member of Hadoop Performance Group}
        \item Designed and implemented a new MapReduce framework, SFMapReduce, for small files storing and processing based on Original Hadoop.
        \item Tested and tuned Hive performance. Translated TPC-DS benchmark to HiveQL. 
        \item {\bf Publication}: {\bf Fang Zhou}, Hai Pham, Jianhui Yue, Hao Zou and Weikuan Yu, ``SFMapReduce: An optimized MapReduce framework for Small Files'', IEEE International Conference on Network, Architecture and Storage (NAS), 2015.
    \end{itemize}

{\bf Visual Intelligent Lab. Harbin, Research Assistant}   \hfill 2010 - 2013
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
        \item {\bf Member of Video Coding Group}
        \item Proposed and implemented a new distortion estimation model for Distributed Video Coding.
        \item Proposed and implemented a downsampled compensation model for video transmission.
    \end{itemize}

\section{Selected\\Projects}
%    {\bf  LISP Interpreter. Columbus, OH}    \hfill   Sept.2015 - Oct.2015 \\
%        An advanced programming language project
%    \begin{itemize}[leftmargin=\bulletindent]
%       \itemsep -2pt
%        \item Designed and built an interpreter for a LISP-like functional language in \CC{} on Linux
%        \item Implemented a recursive descent Parser and Evaluator expressed in tree-like structure
%    \end{itemize}

    {\bf Small File MapReduce Processing Framework. Auburn, AL}	\hfill   Dec.2013 - May.2015 \\
    An advanced big data processing project.
	\begin{itemize}[leftmargin=\bulletindent]
		\itemsep -2pt
			\item Proposed a storage solution for small files to solve the memory pressure on the NameNode.
    	\item Designed the corresponding MapReduce class to process small files efficiently. 
    	\item Implemented new specific RecordReader and InputSplit class in Hadoop/Yarn.
	\end{itemize}


    {\bf Two Layer Scheduler in Hive. Auburn, AL}	\hfill   Dec.2013 - May.2015 \\
    An advanced big data application project.
	\begin{itemize}[leftmargin=\bulletindent]
		\itemsep -2pt
			\item Translated 20+ original TPC-DS SQL queries into HiveQL queries.
    	\item Tested the Hive performance with the new two layer scheduler. 
    	\item Wrote bash scripts and HiveQL queries.
	\end{itemize}

    {\bf FaceCollect Project. Auburn, AL}	\hfill   Aug.2014 - Oct.2014 \\
    A data fetching and collecting project.
	\begin{itemize}[leftmargin=\bulletindent]
		\itemsep -2pt
			\item Designed a framework to collect the data for a customer behaviour research group.
			\item Used Facebook APIs to fetch the posts and reviews from the public homepage in Facebook.
    	\item Implemented the program in Java and Python. 
	\end{itemize}

    {\bf Mine Sweeping Game. Harbin, China}	\hfill   Aug.2011 - Oct.2011 \\
    An android game project. 
	\begin{itemize}[leftmargin=\bulletindent]
		\itemsep -2pt
			\item Designed a mine sweeping game for the android phones and tablets.
			\item Published the game on a third-party Android Market (GFan Market), which has been downloaded 2000+ times.
    	\item Implemented the program in Java with Eclipse. 
	\end{itemize}

\section{Skills}
   \begin{tabular}{l p{5in}}
    Languages: & Java, Python, C, Bash, JavaScript, Delphi, \CC{}. \\
    Frameworks: & Hadoop/Yarn, Spark, Spark SQL, Hive, Accumulo, MySQL, PostgreSQL.\\
    Tools:     & Vim, Git, Eclipse, Xcode, Sublime Text. \\
   \end{tabular}

\end{resume}
\end{document}

