% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[11pt,margin,line]{res}

\textwidth=6.3in
\textheight=10.45in
\sectionskip=0.12in
\parskip=0.12in
\addtolength{\oddsidemargin}{-0.475in}
\addtolength{\topmargin}{-.775in}

\usepackage{hyperref}
\usepackage{enumitem}

\newcommand{\bulletindent}{11pt}
\newcommand{\CC}{C\nolinebreak\hspace{.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}

\begin{document}

\name{\LARGE\bf Xiaoye Cheng}

\begin{resume}

\section{Contact}
%\href{github.com/t1mch0w/}{https://github.com/t1mch0w/}
\hfill \href{mailto:xc37@indiana.edu}{xc37@indiana.edu} \hfill (812)-327-9601  %\hfill 3209 E 10th St., Apt D24, Bloomington, IN, 47408 

\section{Education}
{\bf Indiana University Bloomington.} Bloomington, IN       \hfill 2015 - Present\\
{\bf Ph.D. in Information System}  \hfill Expected May.2020

{\bf Auburn University.} Auburn, AL \hfill 2013 - 2015\\
{\bf Ph.D. in Information System Management}, GPA 3.79/4 

{\bf Harbin Institute of Technology.} Harbin, China \hfill 2010 - 2012\\
{\bf M.M. in Management Science and Engineering}, GPA: 86.22/100 

{\bf Northeastern University.} Shenyang, China \hfill 2006 - 2010\\
{\bf B.M. in Management Information System}, GPA: 84.78/100

\section{Honors\\Awards}
Department fellowship in IUB \hfill 2015 - 2016\\
Top-class scholarship in HIT \hfill 2011 - 2012\\
First-class scholarship in HIT \hfill 2010 - 2011\\
Recommended for admission to HIT for a master degree \hfill 2009\\
First-class or second-class scholarship in NEU \hfill 2006 - 2010\\
Entered the super class in NEU (the top class in School) \hfill 2006

\section{Publications}
{\bf An Examination of Big Data Capabilities in Creating Business Value}\\
S Sun, S Zhu, {\bf X Cheng}, T Byrd\\
Decision Sciences Institute (DSI), 2015

{\bf The Effect of Different Moral Perspectives on Moral Judgment}\\
J Song, BE Larson, {\bf X Cheng}, JR Drake, DJ Hall\\
Decision Sciences Institute (DSI), 2014

{\bf Use of Serious Games in a Data Communications and Networking Management Course}\\
{\bf X Cheng}, Y Wang, C Sankar\\
Submitted to the journal {\bf Computers and Education}.

\section{Research\\Experience}
{\bf Researching on Improving The Accuracy of Recommedation Systems Using Personality Traits and Rating Behavior} \hfill 2015 - Present\\
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
        \item Analyze personality traits and rating behavior based on online reviews.
    \end{itemize}
{\bf Researching on Use of Serious Games in a Data Communications and Networking Management Course} \hfill 2014 - Present\\
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
        \item Use mix methods to examin the effects of several serious games on students’ learning experience, focusing particularly on concentration and enjoyment, as well as measuring the perceived improvement in their Higher-order Cognitive Skills (HOCS). 
        \item Conclude features of serious games such as the challenge they present and their perceived ease of use and usefulness have positive effects on students’ concentration and enjoyment, and this learning experience did indeed significantly improve their perceived HOCS.
    \end{itemize}

{\bf Researching on Factors that Affect Online Sales Promotion Recommendation Popularity} \hfill 2014 - Present\\
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
        \item Explore the successful factors of the current hot online shopping assistant – sales promotion recommendation websites from the aspect of organization.
        \item Analyze factors of sales promotion strategy, product features and website recommendation intensity that may have effects on the popularity of sales promotion recommendation based on literatures.
        \item Writing codes with Java to collect online information on sales promotion recommendation websites.
    \end{itemize}

{\bf Researching on Factors that Influence Brand Post Popularity in Social Network: An Experimental Research Based on Panel Data} \hfill 2014 - Present\\
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
        \item Build research model based on a dynamic and chronological effects of online word-of-mouth on the popularity of brand posts in Facebook. At the same time, take other factors related to brand posts into consideration of model building.
        \item Collected time sequential data from Facebook.com by using Facebook API and Java
    \end{itemize}

{\bf Researched on The Impact of Automobiles Online Word-of-Mouth (WOM) on Consumer Purchasing Behavior} \hfill 2012
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
        \item Wrote programming to download mass data of information of automobiles, sales and online customer reviews on the biggest automobile website in China (https://www.auto.sina.com).
        \item Established cross-sectional data and panel data model.
        \item Empirically analyzed the influence of the automobiles’ online WOM on consumer purchasing behavior using collected data.
        \item Published a paper titled ``The Effect of Different Moral Perspectives on Moral Judgment" as the third author in 2014 DSI Annual Meeting.
    \end{itemize}

{\bf Researched on The Evaluation of the Liquidity of Stock Index Futures Market in China} \hfill 2010
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
				\item Collected materials about present study and methods used by foreign stock index futures markets.
				\item Designed indicates of liquidity according to stock index futures market in China.
    \end{itemize}

\section {Activities}
    \begin{itemize}[leftmargin=\bulletindent]
        \itemsep -2pt
				\item External reviewer for Americas Conference on Information Systems (AMCIS 2014)
				\item Participated in an English Book ``Introduction to Information Systems", 2010
    \end{itemize}


\section{Selected\\Projects}
    {\bf FaceCollect Project. Auburn, AL}	\hfill   Aug.2014 - Oct.2014 \\
    A data fetching and collecting project.
	\begin{itemize}[leftmargin=\bulletindent]
		\itemsep -2pt
			\item Designed a framework to collect the data for a customer behaviour research group.
			\item Used Facebook APIs to fetch the posts and reviews from the public homepage in Facebook.
    	\item Implemented the program in Java and Python. 
	\end{itemize}


    {\bf Mine Sweeping Game. Harbin, China}	\hfill   Aug.2011 - Oct.2011 \\
    An android game project. 
	\begin{itemize}[leftmargin=\bulletindent]
		\itemsep -2pt
			\item Designed a mine sweeping game for the android phones and tablets.
			\item Published the game on a third-party Android Market (GFan Market), which has been downloaded 2000+ times.
    	\item Implemented the program in Java with Eclipse. 
	\end{itemize}

    {\bf Management Information System Website. Shenyang, China}	\hfill   Aug.2009 - Dec.2009 \\
    A information system project.
	\begin{itemize}[leftmargin=\bulletindent]
		\itemsep -2pt
			\item Designed and implemented a sales management information system on website independently. 
			\item Implemented management functions applying ASP technology.
			\item Collected data of different products from the website of the company and stored the data in an Access database.
	\end{itemize}

\section{English\\Proficiency}
	\begin{itemize}[leftmargin=\bulletindent]
	\item {\bf GMAT}: Total 730, Quantitative 51, Verbal 37.
	\item {\bf TOEFL (iBT)}: Total 100, Reading 26, Listening 27, Speaking 19, Writing 28.
	\end{itemize}

\section{Computer\\Skills}
	\begin{itemize}[leftmargin=\bulletindent]
	\item Skilled in applying data analysis and statistical software such as Eviews, SPSS, R, and STATA.
	\item Skilled in using various types of program languages such as JAVA, Python, C, ASP.net and Delphi.
	\item Practiced well in UML, Dreamweaver and Database (Access \& SQL Server).
%	\item Obtained National Computer Rank Examination Certificate for Grade 2 (C Language) and Grade 3 (network techniques).
%	\item Proficient in using Microsoft applications such as Word, Excel and PowerPoint.
	\end{itemize}
\end{resume}
\end{document}

